### 2009-11-09 doc/tech_doc/a-rex/arex_tech_doc.tex
more clarifications in cache doc

At the start of a file download, the cache file is locked, so that
it cannot be deleted and so that another download process cannot write
the same file simultaneously. This done by creating a file with the
same name as the cache filename but with a \emph{.lock} suffix. This
file contains the process ID of the process and the hostname of the
host holding the lock. If this file is present, another process cannot
do anything with the cache file and must wait until the cache file
is unlocked (i.e. the \emph{.lock} file no longer exists). The lock
has a timeout of one day, so that stale locks left behind by a download
process exiting abnormally will eventually be cleaned up. Also, if
the process corresponding to the process ID stored inside the lock
is no longer running on the host specified in the lock, it is safe
to assume that the lock file can be deleted.

@@

If a job requests an input file which can be cached or is allowed to
be cached, it is stored in the selected cache directory, and depending
on the configuration, either the file is copied to the SD or a hard
link is created in a per-job directory and a soft link is created in
the SD to there. The per-job directories are in the \emph{joblinks}
subdirectory of the main cache directory. The former option is advised
if the cache is on a file system which will suffer poor performance
from a large number of jobs reading files on it, or the file system
containing the cache is not accessible from worker nodes. The latter
option is the default option. The per-job directory is only readable
by the local user running the job, and the cache directory is readable
only by the A-REX user (usually root). This means that the local user
cannot access any other users' cache files. It also means that cache
files can be removed without needing to know whether they are in use
by a currently running job.

@@

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which the notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finished (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7 days for \emph{ttl} and 30 days for \emph{ttr}.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by usingon
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path} -- specifies path to the directory
in which the SD is created. If the path is {*} the default one is
used -- \textit{\$HOME/.jobs}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} - specifies
a directory to store cached data (see section \ref{sec:cache}). Multiple
cache directories may be specified by specifying multiple \emph{cachedir}
commands. Cached files will be distributed evenly between the caches.
Specifying no \emph{cachedir }command or commands with an empty path
disables caching. Optional \textit{link\_path} specifies the path
at which \emph{path} is accessible on computing nodes, if it is different
from the path on the A-REX host. If \textit{link\_path} is set to '.'
files are not soft-linked, nor are per-job links created, but files
are copied to the session directory.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} - specifies
high and low watermarks for space used by each cache, as a percentage
of the space on the file system on which the cache directory is located.
When the max is exceeded, files will be deleted to bring the used
space down to the min level. It is a good idea to have each cache
on its own separate file system. To turn off this feature, \char`\"{}cachesize\char`\"{}
without parameters can be specified. These cache settings apply to
all caches specified by \emph{cachedir} commands.
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. Actual
number is provided in job description and defaults to 0.
\end{itemize}

>>>>

At the start of a file download, the cache file is locked, so that
it cannot be deleted and so that another download process cannot write
the same file simultaneously. This is done by creating a file with the
same name as the cache filename but with a \emph{.lock} suffix. This
file contains the process ID of the process and the hostname of the
host holding the lock. If this file is present, another process cannot
do anything with the cache file and must wait until the cache file
is unlocked (i.e. the \emph{.lock} file no longer exists). The lock
has a timeout of one day, so that stale locks left behind by a download
process exiting abnormally will eventually be cleaned up. Also, if
the process corresponding to the process ID stored inside the lock
is no longer running on the host specified in the lock, it is safe
to assume that the lock file can be deleted.

@@

If a job requests an input file which can be cached or is allowed to
be cached, it is stored in the selected cache directory, and depending
on the configuration, either the file is copied to the SD or a hard
link is created in a per-job directory and a soft link is created in
the SD to there. The per-job directories are in the \emph{joblinks}
subdirectory of the main cache directory. The former option is advised
if the cache is on a file system which will suffer poor performance
from a large number of jobs reading files on it, or the file system
containing the cache is not accessible from worker nodes. The latter
option is the default option. The per-job directory is only readable
by the local user running the job, and the cache directory is readable
only by the A-REX user. This means that the local user cannot access
any other users' cache files. It also means that cache files can be
removed without needing to know whether they are in use by a currently
running job. Note that when running A-REX under a non-privileged user
account, all cache files will be owned and accessible by the same
user, and therefore modifyable by running jobs. This is potentially
dangerous and so cacheing should be used with caution in this case.

@@

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which the notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finished (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7 days for \emph{ttl} and 30 days for \emph{ttr}.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by usingon
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path} -- specifies path to the directory
in which the SD is created. If the path is {*} the default one is
used -- \textit{\$HOME/.jobs}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} - specifies
a directory to store cached data (see section \ref{sec:cache}). Multiple
cache directories may be specified by specifying multiple \emph{cachedir}
commands. Cached files will be distributed evenly between the caches.
Specifying no \emph{cachedir }command or commands with an empty path
disables caching. Optional \textit{link\_path} specifies the path
at which \emph{path} is accessible on computing nodes, if it is different
from the path on the A-REX host. If \textit{link\_path} is set to '.'
files are not soft-linked, nor are per-job links created, but files
are copied to the session directory.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} -
  specifies high and low watermarks for space used on the file system
  on which the cache directory is located, as a percentage of total
  file system capacity/ When the max is exceeded, files will be
  deleted to bring the used space down to the min level. It is a good
  idea to have each cache on its own separate file system. To turn off
  this feature, \char`\"{}cachesize\char`\"{} without parameters can
  be specified. These cache settings apply to all caches specified by
  \emph{cachedir} commands.
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. Actual
number is provided in job description and defaults to 0.
\end{itemize}
